%\subsection*{PSU Power Engineering Laboratory}
%\noindent\small{Lab description...}

\section*{Authors}
\phantomsection
\addcontentsline{toc}{section}{Authors}
\noindent\textcolor{PSUblue}{\textbf{Adam A. Dezay}}\small{ is a recent BS Electrical Engineering graduate from Portland State University. Adam works for Analog Devices at the time of publishing} 

\noindent\textcolor{PSUblue}{\textbf{Manuel A. Garcia}}\small{ is a recent BS Electrical Engineering graduate from Portland State University. Manuel is pursuing his dream of becoming a stay at home father with great success so far.} 

\noindent\textcolor{PSUblue}{\textbf{Brandon P. Hippe}}\small{ is a recent BS Computer Engineering graduate from Portland State University. Brandon is seeking to complete his masters after graduation, and continue his research with the WEST Lab.  } 

\noindent\textcolor{PSUblue}{\textbf{Mercedes C. Newton}}\small{ is a recent BS Electrical Engineering graduate with a Minor in mathematics from Portland State University. Mercedes has accepted a position as an Electrical Engineer at Jacobs engineering starting in July of 2023.} 


\section*{Acknowledgements}
\phantomsection
\addcontentsline{toc}{section}{Acknowledgements}
\noindent\small{The authors would like to acknowledge their Industry Sponsor Dr. David C. Burnett and their Faculty Advisor Dr. John M. Acken for their commitment to both the project and our team's growth.}  

\section*{Disclaimer}
\phantomsection
\addcontentsline{toc}{section}{Disclaimer}
\noindent\small{The contents of this report reflect the views of the authors, who are solely responsible for the facts and the accuracy of the material and information presented herein.  This document is disseminated in the interest of information exchange.