In retrospect, we feel our project was very successful. Our team was able to collaborate in order to execute this project. Our team played to each of our specific talents which made for an excellent work environment.

Our team faced a variety of challenges in regards to using MSP430s, SmartMesh, enclosure building and PCB design. Connecting each team member to their respective MSP430 proved to be more challenging than many of us had anticipated. Documentation surrounding MSP430 was scarce and oftentimes unhelpful. Most of our team members needed to delete Energia files and redownload before each use to connect with the MSP430. SmartMesh also had many problems that previous teams have not encountered. Our original ultrasonic anemometer proved to be much harder to work with which is why we switched to the hotwire option despite the huge discrepancy in power use.

The combination of all these problems and our approach to doing each part separately proved unfruitful as we had not built a prototype by the midpoint of the timeline. This is when we switched to dedicating a set time to work on the project weekly, in person, as a team. This proved to accelerate our progress as it allowed us to help each other at roadblocks. We also learned that some of our MSP430s were much more prone to having issues than others. This allowed us to rapidly prototype a working node on the fastest system and MSP430. This also allowed different members to shift rapidly to complete auxiliary projects like reports and presentations.

Many thanks to our industry sponsor and faculty advisor who requested that we present our progress a several times throughout our project as well as requesting an updated Gantt chart weekly. This allowed us to compile our progress and have a clear path at a glance. Weekly meetings with at least 1 of the advisor or sponsor also proved necessary to work through a multitude of problems and is credited to keeping us working on the requirements. 

Documentation was something that we excelled at throughout the project. Notes of weekly meetings were documented on the team’s Trello board. Weekly reports and any documentation was copied to the team’s Google Drive, Github repository, Trello board, and emailed to the advisor and sponsor. We also built a website to host some of this information.
